%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Alicia Sykes CV LaTeX Template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{resume-format}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    \headerfirstnamestyle{ Chris } \headerlastnamestyle{ Xedis } \\
    \vspace{2mm}
    {\faEnvelope\ chris@voidxedis.com} | {\faMapMarker\ Las Vegas, NV} | {\faLink\ \href{ https://dashy.xedis.net }{ https://dashy.xedis.net }}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Statement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{cvpersonalstatement}
  \item { Dynamic and adaptable professional with over 2 decades of experience in technology.  Specializing in security, Point of Sale (POS) integration, video and audio streaming and recording. Proven track record in leading development and deployment of cybersecurity standards across extensive production assets. Passionate about continuous learning and tackling new challenges in fast-paced environments. Skilled at breaking broken things worse to fix them, sharing the lessons learned. }
\end{cvpersonalstatement}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}
\begin{cventries}
    \cventry
    { Production Security Architect }
    { DTiQ }
    {}
    { December 2022 – August 2024 }
    {\begin{cvitems}
        \item { Championed security thinking and ensured solutions were deployed within budget constraints }
        \item { Conducted compliance assessments against the CIS Controls, PCI and beginnings of ISO 27000 series. }
        \item { Designed a robust 5-year Security plan that could be worked into the development roadmap. }
        \item { Established effective communication channels to enhance security awareness. }
        \item { Implemented solutions that had minimal negative impact to internal/external customers. }
        \item { Managed and resolved security incidents. }
        \item { Oversaw continuous security monitoring of edge devices and unified OS patches across diverse hardware. }
        \item { Participated in penetration testing and drove secure code practices through creative collaboration. }
        \item { Provided live demonstrations with practical real-world scenarios to show leadership the real world risk the initiatives resolved. }
    \end{cvitems}}
    \cventry
    { Advanced Technology Manager }
    { DTiQ }
    {}
    { July 2018 – August 2024 }
    {\begin{cvitems}
        \item { Advised CIO/CTO/CEO on complex technical issues. }Chris-Xedis-CV.pdf
        \item { Created roadmaps, optimized processes, and conducted compliance and security maintenance audits. }
        \item { Effective resolver of escalations both within my team and across the enterprise. Was an “In the trenches” Technical Manager. }
        \item { Established effective pipelines for process development by leading cross-department bridge-building }
        \item { Facilitated integration post-acquisition, led new platform onboarding, and migrated existing hardware. }
        \item { Mastered POS integration and application management. }
        \item { Provided Executive Level Summaries along with relevant context and details just in case a nuance was overlooked. }
        \item { Reported directly to the CTO. Advanced Technology Group (ATG) was similar to Office of the CTO elsewhere. }
    \end{cvitems}}
    \cventry
    { Systems Analyst }
    { DTiQ }
    {}
    { March 2017 – July 2018 }
    {\begin{cvitems}
        \item { Created automation solutions to enhance existing processes. }
        \item { Developed, tested, and deployed software updates in a medium to large production environment. }
        \item { Trained teams on proprietary technology and solutions, providing leadership and development coaching. }
        \item { Generated extensive knowledgebase documentation. }
    \end{cvitems}}
\end{cventries}

    \vspace{-5mm}
    \begin{flushright}
        \small\color{lightgray} \href{ https://linkedin.com/in/xchrisx }See all previous roles at linkedin.com/in/xchrisx
    \end{flushright}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Achievements}
\begin{cvachievements}
    \item { Designed and deployed Wazuh cluster to AWS and wrote a python package to install Wazuh agent paired with Sysmon on 15k production assets across the globe. }
    \item { Found creative ways to inspire secure thinking throughout the SDLC; From Planning to Maintaining; incl but not limited to; Production Deployments, Edge Device Image Creation, Auth creation,handling and storage. }
    \item { Led a team of highly skilled unique characters, rejects and problem children, harnessing their powers for the greater good of the company rising to the go to team when things hit the fan and needed outside of process thinking. }
    \item { All my knowledge and skills have been acquired through either self study, self driven experimentation, or in production environent escalations and dumpster fires. Autodidact, I can learn anything I need to learn in order to achieve my task at hand. }
\end{cvachievements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\vspace{-2mm}


\cvsection{Skills}
\begin{cventries}
    \cventry
    {}
    {\def\arraystretch{1.15}{\begin{tabular}{ l l }
        Security:  & {\skill{ Wazuh, Sysmon, RITA, AC Hunter, Netdata, Elastic Agent, Nmap, Wireshark, ZAP, Burpsuite, Metasploit }} \\
        Scripting:  & {\skill{ Python, Bash }} \\
        Compliance:  & {\skill{ PCI 4.0.1, CIS Controls 8.1, NIST, ISO/IEC 27000 }} \\
        Production:  & {\skill{ ProxMox, Nginx, Docker, Grafana, Prometheus, MSSQL, MySQL/MariaDB, SQLite3 }} \\
        Cloud:  & {\skill{ AWS, Google Cloud, Runpod }} \\
        AWS Security:  & {\skill{ Cloudtrail/CloudWatch, Detective, Security Hub, IAM, IAM Identity Center, KMS }} \\
        AWS Infrastructure:  & {\skill{ Control Tower, Cloudformation, Athena, Elastic Container Registry, Organizations, Config }} \\
        Web Platforms:  & {\skill{ Shopify, Google Analytics, Umami, GitHub (Personal and Enterprise), Meta (FB and IG), Squarespace }} \\
    \end{tabular}}}
    {}
    {}
    {}
\end{cventries}

    \vspace{-10mm}
    \begin{flushright}
        \small\color{lightgray} \href{ https://dashy.xedis.net/home/homelab }See example projects built with some of the technology at https://dashy.xedis.net/home/homelab
    \end{flushright}



\vspace{-7mm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Footer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add the footer link at the end of the document
\vspace{10mm}
\begin{flushleft}
    \tiny\color{lightgray} \href{https://github.com/xedis/cv}{ View CV source at github.com/xedis/cv}
\end{flushleft}
\ 
\end{document}